A sheaf--function dictionary for algebraic tori over local fields

### 2013-10-06 shanghai.tex
Minor improvements to Section 6.

Now we localize $C(G)$.
Let us say that $(g,T)$ in $C(G)$ is a \emph{weak isomorphism} if $g$ is surjective
and $T$ is an isomorphism of vector spaces.
\Clifton{Should this be another lemma in this section?}
The set $W$ of weak isomorphisms in $C(G)$
is a saturated, left multiplicative system in $C(G)$ in the sense of
  \cite{kashiwara-schapira:CatgoriesSheaves}*{Defs 7.1.5, 7.1.19}.
Let \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at $W$.
A morphism in $C(G)[W^{-1}]$ is an equivalence class of a diagram
  \begin{equation}\label{eq:morGCf}
   \begin{tikzcd}[column sep=50]
   (f,\psi) \arrow{r}{(g_1,T_1)} & (f_1,\psi_1) & \arrow[swap]{l}{(h_1,U_1)} (f',\psi')
   \end{tikzcd}
  \end{equation}
 where $(g',T') : (f,\psi) \to (f',\psi')$ is any map in $C(G)$ 
 and $(h_1,U_1) :  (f',\psi') \to (f_1,\psi_1)$ is a weak isomorphism in $C(G)$; see \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16} for more detail, including the equivalence relation mentioned above.
%Likewise, $C(G)[W^{-1}]$ is a tensor category.

@@

For general $G$, there are bounded quasicharacter sheaves which are not finite.  Identifying
$\QCf(G)$ with its image under $B_G \circ L_G$, as defined in Proposition~\ref{prop:BG} and in the proof of Proposition~\ref{prop:bounded}, we will see in Corollary~\ref{cor:bounded-and-finite} that
a quasicharacter sheaf is finite if and only if its trace of Frobenius has finite image.

>>>>

Now we localize $C(G)$.
Let us say that $(g,T)$ in $C(G)$ is a \emph{weak isomorphism} if $g$ is surjective
and $T$ is an isomorphism of vector spaces.
\Clifton{Should this be another lemma in this section?}
The set $W$ of weak isomorphisms in $C(G)$
is a saturated, left multiplicative system in $C(G)$ in the sense of
  \cite{kashiwara-schapira:CatgoriesSheaves}*{Defs 7.1.5, 7.1.19}.
Let \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at $W$.
A morphism in $C(G)[W^{-1}]$ is an equivalence class of a diagram
%  \begin{equation}\label{eq:morGCf}
\[   
\begin{tikzcd}[column sep=30]
   (f,\psi) \arrow{r}{(g,T)} & (f',\psi') & \arrow[swap]{l}{(h,U)} (f_1,\psi_1)
   \end{tikzcd}
\]
%  \end{equation}
 where $(g,T) : (f,\psi) \to (f',\psi')$ is any map in $C(G)$ 
 and $(h,U) :  (f',\psi') \to (f_1,\psi_1)$ is a weak isomorphism in $C(G)$; see \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16} for more detail, including the equivalence relation mentioned above.
%Likewise, $C(G)[W^{-1}]$ is a tensor category.

@@

On general $\QC$-schemes $G$, there are bounded quasicharacter sheaves which are not finite.  Identifying
$\QCf(G)$ with its image under $B_G \circ L_G$, as defined in Proposition~\ref{prop:BG} and in the proof of Proposition~\ref{prop:bounded}, we will see in Corollary~\ref{cor:bounded-and-finite} that
a quasicharacter sheaf is finite if and only if its trace of Frobenius has finite image.
